### 2009-11-29 doc/tech_doc/janitor/tex_installation/installation.tex
only invoke janitor if it's enabled in the config
Added symbolic link for compatibility until the tech-doc/janitor directory is removed.

\chapter{Installation}

% ** Dependencies
% *** Ordinary: log4perl and ``Redland RDF Library - Perl Interface''
% *** WebService: libperl-dev
% *** Protege: For maintaining the knowledge base

The Janitor requires the two perl packages listed in
table~\ref{tab:install_dependencies}. To have
the WebService interface for the Janitor, the packages listed in the
table~\ref{tab:install_dependencies_optional} need to be installed before
the build process is. The Perl modules are available on CPAN and ship
with all major Linux distributions.

\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for Janitor.}{Log4perl is used for the internal logging of Janitor, while the 
                   Redland RDF library is used for accessing the knowledge base of Runtime Environments.}
        \label{tab:install_dependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for Janitor.}{The library libperl-dev provides header files which are needed to link the 
                   WebService to the Perl interpreter.}
        \label{tab:install_dependencies_optional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

The Janitor will be installed by default along with ARC1. Support for
the dynamic REs can be completely disabled at compile time by using
the \textit{configure} flags \textit{--disable-janitor-service} for
the complete janitor or \textit{--disable-janitor-webservice} to only
disable the Janitor's Web Service.

Furthermore it is recommended to install the ontology editor 
Prot\`eg\`e\footnote{\href{http://protege.stanford.edu}{http://protege.stanford.edu}} in order to be to easily maintain the 
knowledge database of installable packages. At the time of writing, no Linux distribution is offering packages for this fine tool.

\section{Configuration}\label{sec:janitor_configuration}

The current version of the Janitor can be configured using the common file \textit{arc.conf}. It is expected in the 
configuration directory \textit{etc}. The Janitor is using the environment variable \textit{NORDUGRID\_CONFIG}
to determine the location of the corresponding file. If that variable is not set, the default location \textit{/etc/arc.conf} will be used. 
The configuration is assigned by the section \lbrack janitor\rbrack. Table~\ref{tab:arc_conf_tags} describes the available tags
for Janitor's configuration.

\begin{landscape}
\begin{table}[!h]
   \begin{center}
        \mycaption{Tags usable in \textit{arc.conf} within the section janitor.}{Tags usable in \textit{arc.conf} within the section janitor.}
	\label{tab:arc_conf_tags}
	\begin{longtable}{|p{3cm}|p{10cm}||p{10cm}|}
	\hline
	   \textbf{tag}    & \textbf{example}                      & \textbf{description}\\
        \hline
           enabled         & "1"                                   & Boolean flag which enables or disables janitor in A-REX.\\
	   uid             & "root"                                & The effective uid. \\
	   gid             & "0"                                   & The effective gid. \\
	   registrationdir & "/var/spool/nordugrid/janitor"        & Directory where we the current states of jobs are kept. \\
	   catalog         & "/var/spool/nordugrid/janitor/catalog/knowarc.rdf"& URL of the catalog containg the package information.\\
	   downloaddir     & "/var/spool/nordugrid/janitor/download" & Directory for downloads \\
	   installationdir & "/var/spool/nordugrid/janitor/runtime"& Directory for installation of packages                   \\
	   jobexpirytime   & "7200"                                & If a job is older than this, it is considered dead and assigned to be removal pending.\\
	   rteexpirytime   & "36"                                  & If a runtime environment was not used for this time, it will be assigned to be removal pending.\\
	   allow\_base     & "*"                                   & Allow rule for base packages. \\
	   deny\_base      & "debian::etch"                        & Deny rule for base packages.\\
	   allow\_rte      & "*"                                   & Allow rule for base packages. \\
	   deny\_rte       & "APPS/MATH/ELMER-5.0.2"               & Deny rule for base packages. \\
	   logconf         & "/opt/nordugrid/etc/log.conf"         & Location of the logging configuration file for janitor.\\
	\hline
	\end{longtable}
   \end{center}
\end{table}
\end{landscape}

The parameter \texttt{enable} specifies whether the Janitor shall be used within A-REX or not. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective the user and group id shall be used for Janitor. 
The \texttt{registrationdir} describes the directory in which the subdirectories \texttt{jobs} and \texttt{rtes} will be created.
In these directories the states of the jobs and the runtime environments will be stored. 
The knowledge base of installable packages is specified by the parameter \texttt{catalog}. 
Its value can be any kind of URL pointing to a file written in the Resource Description Framework (RDF) format.
The specification of the RDF file will be explained in detail in section~\ref{sec:catalog}.
The parameter \texttt{downloaddir} assigns the directory in which the installation files will be saved after they have been 
downloaded or copied from the repository which was specified by the catalog. The \texttt{installationdir} finally specifies the
directory into which all packages will be installed and should be 
available for all computing elements, i.e.\ by using a shared volume.
If the configuration file furthermore contains the \texttt{runtimedir} tag within the section \texttt{grid-manager}, the Janitor will also
create a symbolic link in the \texttt{runtimedir} pointing to the configuration script of the installation done by the Janitor.
The tags \texttt{jobexpirytime} and \texttt{rteexpirytime} are used for automated cleanup and is defined in seconds.
The default value for the \texttt{jobexpirytime} is seven days and for the \texttt{rteexpirytime} three days. 
The additional tags \texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and \texttt{deny\_rte} are used to include
or exclude certain base packages or runtime environments of the catalog. This feature is useful, if the catalog is maintained by
a higher organization.
The path to the log4perl configuration file is defined by the tag \texttt{logconf}.
An example how to configure ARC and log4perl is provided in the Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

\lstsetCONFIGURE
\begin{lstlisting}[
        label=lst:arc_conf,
        caption={ [Example \textit{arc.conf} settings for janitor.]
                  \textbf{Example \textit{arc.conf} settings for janitor.}}
        ]
[janitor]
enabled="1"
logconf="/opt/nordugrid/etc/log.conf"
registrationdir="/var/spool/nordugrid/janitor"
installationdir="/var/spool/nordugrid/janitor/runtime"
downloaddir="/var/spool/nordugrid/janitor/download"
jobexpirytime="7200"
rteexpirytime="36"
uid="root"
gid="0"
allow_base="*"
allow_rte="*"

[janitor/nordugrid]
catalog="/var/spool/nordugrid/janitor/catalog/knowarc.rdf"
\end{lstlisting}

\lstsetCONFIGURE
\begin{lstlisting}[
        label=lst:log_conf,
        caption={ [Example \textit{log.conf} settings for janitor.]
                  \textbf{Example \textit{log.conf} settings for janitor.}}
        ]
# Master Loglevel
# [OFF | DEBUG | INFO | WARN | ERROR | FATAL]
#log4perl.threshold = OFF

log4perl.rootLogger = WARN, DebugLog, MainLog, ErrorLog
log4perl.appender.DebugLog = Log::Log4perl::Appender::Screen
log4perl.appender.DebugLog.layout = PatternLayout
log4perl.appender.DebugLog.layout.ConversionPattern = [%C] %d %p> %m%n

log4perl.appender.MainLog = Log::Log4perl::Appender::File
log4perl.appender.MainLog.Threshold = VERBOSE
log4perl.appender.MainLog.filename = /var/log/janitor.log
log4perl.appender.MainLog.layout = PatternLayout
log4perl.appender.MainLog.layout.ConversionPattern = %d %p> %m%n

log4perl.appender.ErrorLog = Log::Log4perl::Appender::File
log4perl.appender.ErrorLog.Threshold = ERROR
log4perl.appender.ErrorLog.filename = /var/log/janitor_error.log

log4perl.appender.ErrorLog.layout = PatternLayout
log4perl.appender.ErrorLog.layout.ConversionPattern = %d %p> %m%n
\end{lstlisting}

% ** Configuring arc.conf
% *** Where to store the data of janitor
% ** Configuring log.conf
% *** Where to store the log of janitor

\section{Limitations}

The Janitor is designed for the usage on Linux distributions.
Its porting to other platforms has not yet been addressed.

The ARC middleware is not ultimately essential for dynamic Runtime Environments.
All the Perl code would be functional with any Grid middleware.

% Is designed for linux distributions. Windows or Mac won't work (Reason wget! maybe also the Executer).

>>>>

../../../manuals/janitor/tex_installation/installation.tex
